### 2025-08-18 chapters/discussion.tex
minor edits

To address overhead and scalability challenges, **enclave multiplexing** offers a promising software-level strategy by consolidating multiple lightweight workloads into a single enclave. This reduces the number of PMP entries required by reusing them across tasks, optimizing resource usage and improving scalability. An example of a multiplexed enclave task dispatcher is shown in Listing~\ref{lst:enclave-mux}.

>>>>

To address overhead and scalability challenges, \emph{enclave multiplexing} offers a promising software-level strategy by consolidating multiple lightweight workloads into a single enclave. This reduces the number of PMP entries required by reusing them across tasks, optimizing resource usage and improving scalability. An example of a multiplexed enclave task dispatcher is shown in Listing~\ref{lst:enclave-mux}.

### 2025-08-18 chapters/system-architecture.tex
minor edits

@@

\begin{lstlisting}[language=bash]
# CPU time: Total time spent in user mode and kernel mode.
# Peak RSS: Maximum resident memory usage during execution.
# Page faults: Number of soft (minor) and hard (major) page faults.
# Context switches: Voluntary and involuntary context switching events.
\end{lstlisting}

>>>>

\begin{lstlisting}[language=bash, caption={CoreMark sample output used to extract IPS}, label={lst:coremark-output}]
2K performance run parameters for coremark.
CoreMark Size    : 666
Total ticks      : 112738928
Iterations/Sec   : 937.43
Iterations       : 100000
\end{lstlisting}

@@

% \begin{lstlisting}[language=bash]
% # CPU time: Total time spent in user mode and kernel mode.
% # Peak RSS: Maximum resident memory usage during execution.
% # Page faults: Number of soft (minor) and hard (major) page faults.
% # Context switches: Voluntary and involuntary context switching events.
% \end{lstlisting}

\begin{lstlisting}[language=C, caption={In-enclave system-level instrumentation using \texttt{getrusage()}}, label={lst:getrusage}]
struct rusage usage;
getrusage(RUSAGE_SELF, &usage);

// CPU time: Total time spent in user mode and kernel mode.
printf("!User CPU time:     %ld.%06lds\n", usage.ru_utime.tv_sec, usage.ru_utime.tv_usec);
printf("!System CPU time:   %ld.%06lds\n", usage.ru_stime.tv_sec, usage.ru_stime.tv_usec);

// Peak RSS: Maximum resident memory usage during execution.
printf("!Max memory (RSS):  %ld KB\n", usage.ru_maxrss);

// Page faults: Number of soft (minor) and hard (major) page faults.
printf("!Minor page faults: %ld\n", usage.ru_minflt);
printf("!Major page faults: %ld\n", usage.ru_majflt);

// Context switches: Voluntary and involuntary context switching events.
printf("!Voluntary context switches:   %ld\n", usage.ru_nvcsw);
printf("!Involuntary context switches: %ld\n", usage.ru_nivcsw);
\end{lstlisting}
